A large-scale analysis of racial disparities in police stops across the

### 2019-07-20 lib/paper_results.Rmd
progress

```{r setup, echo = FALSE}
opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

pfs <- read_rds(here::here("results", "prima_facie_stats.rds"))
vod <- read_rds(here::here("results", "veil_of_darkness.rds"))
disp <- read_rds(here::here("results", "disparity.rds"))
mj <- read_rds(here::here("results", "marijuana_legalization_analysis.rds"))
```

@@

```{r veil_of_darkness-plot}
vod$full$plots$states$time_sliced$`Statewide, TX`
```

```{r veil_of_darkness-mod}
bind_rows(
  vod$dst$coefficients %>% 
    mutate(model = "DST"),  
  vod$full$coefficients %>% 
    mutate(model = "Full year")
) %>% 
  select(model, is_dark, std_error, everything()) %>% 
  kable()
```

@@

\begin{center}
\subsection{Threshold test results}
\end{center}
```{r disparity-city-thresholds-table}
kable(disp$city$threshold$results$aggregate_thresholds)
```
```{r disparity-state-thresholds-table}
kable(disp$state$threshold$results$aggregate_thresholds)
```
\newpage
```{r disparity-city-thresholds-plot, fig.height = 3, fig.width = 7}
disp$city$threshold$plots$aggregate
```
```{r disparity-state-thresholds-plot, fig.height = 3, fig.width = 7}
disp$state$threshold$plots$aggregate
```

\newpage
\begin{center}
\section{Marijuana Legalization Analysis}
\end{center}
```{r mj_table}
kable(mj$tables$search_rate_difference_in_difference_coefficients)
```

>>>>

```{r setup, echo = FALSE}
library(tidyverse)
library(knitr)
opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
pfs <- read_rds(here::here("results", "prima_facie_stats.rds"))
vod <- read_rds(here::here("results", "veil_of_darkness.rds"))
# disp <- read_rds(here::here("results", "disparity.rds"))
mj <- read_rds(here::here("results", "marijuana_legalization_analysis.rds"))
```

@@

```{r veil_of_darkness-plot}
vod$full$plots$states$TX$`6:00pm`
vod$full$plots$states$TX$`6:15pm`
vod$full$plots$states$TX$`6:30pm`
vod$full$plots$states$TX$`6:45pm`
vod$full$plots$states$TX$`7:00pm`
vod$full$plots$states$TX$`7:15pm`
vod$full$plots$states$TX$`7:30pm`
```

```{r veil_of_darkness-main_mod}
vod$dst %>% 
  filter(spline_degree == 6, agency_control, interact_time_loc) %>% 
  kable()
```

```{r veil_of_darkness-appendix_mods}
bind_rows(
  vod$dst %>%
    mutate(model = "DST"),
  vod$full$coefficients %>%
    mutate(model = "Full year")
) %>%
  select(model, agency, is_dark, std_error, everything()) %>%
  kable()
```

@@

\begin{center}
\subsection{Threshold test results}
\end{center}
```{r disparity-city-thresholds-table}
kable(disp$city$threshold$results$aggregate_thresholds)
```
```{r disparity-state-thresholds-table}
kable(disp$state$threshold$results$aggregate_thresholds)
```
\newpage
```{r disparity-city-thresholds-plot, fig.height = 3, fig.width = 7}
disp$city$threshold$plots$aggregate
```
```{r disparity-state-thresholds-plot, fig.height = 3, fig.width = 7}
disp$state$threshold$plots$aggregate
```
\newpage
```{r disparity-city-ppcs, fig.height = 3, fig.width = 7}
disp$city$threshold$ppc$search_rate
```
```{r disparity-state-thresholds-plot, fig.height = 3, fig.width = 7}
disp$city$threshold$ppc$hit_rate
```
\newpage
```{r disparity-state-ppcs, fig.height = 3, fig.width = 7}
disp$state$threshold$ppc$search_rate
```
```{r disparity-state-thresholds-plot, fig.height = 3, fig.width = 7}
disp$state$threshold$ppc$hit_rate
```
\newpage

\begin{center}
\section{Marijuana Legalization Analysis}
\end{center}
```{r mj_table}
kable(mj$tables$search_rate_difference_in_difference_coefficients)
```
